% !TEX root = ./cv_main.tex

\section*{Curriculum Vitae}
\label{sec:cv}


\subsection*{Personal Information}

\begin{tabular}{rl}
	\textsc{Date of birth:} & Wiesbaden, Germany  | April 1st, 1992 \\
	\textsc{Email:}     & \href{gerhard.jung.physics@gmail.com}{\small \url{gerhard.jung.physics@gmail.com}}  \\

\textsc{Homepage:}     & \href{https://gerhardjung.github.io/}{\small \url{https://gerhardjung.github.io/}}, \href{https://scholar.google.com/citations?user=0Wk52qAAAAAJ&hl=en}{\small \url{Google Scholar}}\\
	
\end{tabular}

\subsection*{Main Areas of Research}
Computer simulations in soft matter physics, non-Markovian dynamics, dynamic coarse-graining, machine learning techniques, glass transition, confinement, rheology, non-equilibrium dynamics

%Section: Work Experience at the top
\subsection*{Academic Experience}
\begin{tabular}{r|p{13cm}}
	\textsc{12/2023  }& \textsc{LIPhy, Grenoble (France) } \\-&\emph{Postdoctoral researcher}\\
	Present&\footnotesize{Advisor: Eric Bertin, Misaki Ozawa}\\
	&\footnotesize{Area of study: Decentralized machine learning, statistical physics of social agents}\\		\multicolumn{2}{c}{}\\
		\textsc{10/2021  }& \textsc{CNRS, Montpellier (France) } \\-&\emph{Postdoctoral researcher}\\
	12/2023&\footnotesize{Advisor: Prof. Ludovic Berthier, Prof. Giulio Biroli}\\
	&\footnotesize{Area of study: Glass transition, machine learning, amorphous defects}\\
		\multicolumn{2}{c}{}\\
		\textsc{06/2021  }& \textsc{University of Kyoto (Japan) } \\-&\emph{JSPS Fellow}\\
	\textsc{10/2021  }&\footnotesize{Advisor: Prof. Ryoichi Yamamoto}\\
	&\footnotesize{Area of study: Active particles in viscoelastic media}\\
		\multicolumn{2}{c}{}\\
	\textsc{03/2019  }& \textsc{University of Innsbruck (Austria) } \\-&\emph{Postdoctoral researcher}\\
	\textsc{05/2021}&\footnotesize{Advisor: Prof. Thomas Franosch}\\
	&\footnotesize{Area of study: Glass transition, crystallization, confined geometry}\\
	\multicolumn{2}{c}{}\\
	
		\textsc{05/2018  }& \textsc{Durham University (UK)} \\\textsc{}-&\emph{Visiting researcher}\\10/2018&\footnotesize{  Advisor: Prof. Suzanne Fielding }\\
	&\footnotesize{Area of study: Soft glassy materials, yielding transition, rheology}\\
	\multicolumn{2}{c}{}\\
	
	\textsc{10/2014 }& \textsc{University of Mainz (Germany) } \\\textsc{}-&\emph{Doctoral and postdoctoral researcher}\\02/2019 &\footnotesize{Advisor: Prof. Friederike Schmid}
	\\&\footnotesize{Area of study: Non-Markovian dynamics, systematic coarse-graining, rheology, nonequilibrium
		dynamics}
	\\\multicolumn{2}{c}{}
	

	
\end{tabular}

%Section: Education
\subsection*{Education}
\begin{tabular}{r|p{14cm}}	
	
		\textsc{01/10/2014 }& \textsc{University of Mainz } \\\textsc{}-&\emph{Doctor rerum naturalium} (fast-track program )\\ 13/12/2018&\footnotesize{Advisor: Prof. Friederike Schmid}
	\\&\footnotesize{Thesis title: \emph{`Frequency-dependent phenomena and memory in soft matter systems.'}}
	\footnotesize{Grade: 0.7 (\emph{summa cum laude})}
	\\\multicolumn{2}{c}{}\\
	
		\textsc{21/12/2017}& \textsc{University of Mainz } \\\textsc{}&\emph{Master of Science}\\&\footnotesize{Advisor: Prof. Friederike Schmid}
	\\&\footnotesize{Thesis title: \emph{`Frequency-dependent hydrodynamic interaction between two
			solid spheres.'}}
	\footnotesize{Grade: 1.0}
	\\\multicolumn{2}{c}{}\\
	
	\textsc{24/10/2011}& \textsc{University of Mainz } \\ - &\emph{Bachelor of Science}\\15/08/2014&\footnotesize{Advisor: Prof. Friederike Schmid}
\\&\footnotesize{Thesis title: \emph{`Phase diagrams of model lipid bilayers.'}}
\footnotesize{Grade: 1.0 (\emph{with distinction})}
\\\multicolumn{2}{c}{}\\
	

	\textsc{12/08/2002 } &  \textsc{Gymnasium Eltville}\\
		- &  \emph{High School}\\
		07/06/2011 &
	
\end{tabular}


\subsection*{Awards}
\begin{tabular}{rp{14cm}}
	\textsc{2021:}& JSPS `short-term postdoctoral fellowship'\\
		\textsc{2019:}& \emph{Dr. rer. nat.} with `summa cum laude'\\
\textsc{2016 - 2019:}& {Member of the ‘Graduate School of Excellence Materials Science in Mainz’
 } \\

 \textsc{2013 - 2015:} & {Admission to the ‘Studienstiftung des deutschen Volkes’ (scholarship)} \\

\textsc{2013 - 2014:}& {Recipient of the ‘Deutschlandstipendium’ (scholarship)
}
\\\multicolumn{2}{c}{}\\
	
\end{tabular}

\subsection*{Teaching and Mentoring}
\begin{tabular}{r|p{13cm}}
	\textsc{Lecturer}& {Advanced statistical physics
	} 
	\\\multicolumn{2}{c}{}\\
	\textsc{Tutorials}& Mathematical methods of physics, modelling (computer science), statistical
	physics, electrodynamics, computer simulations in statistical physics
	\\\multicolumn{2}{c}{}\\
	
	\textsc{Supervisor}& {Co-supervision of one PhD student}\\
	& {Co-supervision of one Master student}\\
	& {Supervision of two Bachelor students and one Master student}
	\\\multicolumn{2}{c}{}\\	
\end{tabular}

\subsection*{Organization of Academic Events}

	\begin{tabular}{rl}
			2022: & {AISSAI} Workshop on `Machine Learning Glassy Dynamics'  (5 days)\\
			2018: & CECAM workshop on ‘Dynamic coarse-graining and memory effects in soft matter systems” (2 days)\\
	2017: & SFB TRR146 students retreat (5 days)
	 
\end{tabular}

%Section: Languages
\subsection*{Languages}
\begin{tabular}{rl}
	\textsc{English:}& fluent\\
	\textsc{German:}& mother tongue\\
	\textsc{French:}& advanced 
\end{tabular}

\subsection*{Publications}


\subsubsection*{Publications in peer-reviewed journals}

\begin{enumerate}
	\item Dynamic heterogeneity at the experimental glass transition predicted by transferable machine learning (\textbf{Editor's Suggestion}) \\
	\textbf{G. Jung}, G. Biroli, L. Berthier,  \emph{Phys. Rev. B}, \textbf{109}, 064205 (2024)
	
	\item Mobility, response and transport in non-equilibrium coarse-grained models  (Invited Special Issue: \emph{Non-Markovian Effects in Nonequilibrium Systems})\\
	\textbf{G. Jung}, \emph{J. of Phy. A: Math. and Theo.} \textbf{57}, 095004 (2024) 
	
	\item Force renormalization for probes immersed in an active bath\\
	J. Shea, \textbf{G. Jung}, F Schmid, arXiv:2310.02683, \emph{Soft Matter} \textbf{20}, 1767 (2024)
	
	\item Noise-cancellation algorithm for simulations of Brownian particles\\
	R. Rusch, T. Franosch, \textbf{G. Jung}, \emph{Phys. Rev. E} \textbf{109}, 015303 (2024)
	
	\item Dynamic coarse-graining of linear and non-linear systems: Mori–Zwanzig formalism and beyond\\
	B. Jung, \textbf{G. Jung}, \emph{J. Chem. Phys.} \textbf{159}, 084110 (2023)
	
	\item Direct numerical simulations of a microswimmer in a viscoelastic fluid\\
	T. Kobayashi, \textbf{G. Jung}, Y. Matsuoka, Y. Nakayama, JJ. Molina, R. Yamamoto, \emph{Soft Matter} \textbf{19}, 7109 (2023)
	
	\item  Predicting dynamic heterogeneity in glass-forming liquids by physics-inspired machine learning\\
	\textbf{G. Jung}, G. Biroli, L. Berthier, \emph{Phys. Rev. Lett.} \textbf{130}, 238202 (2023) 
	
	\item  Computer simulations and mode-coupling theory of glass-forming confined hard-sphere fluids\\
	\textbf{G. Jung}, T. Franosch, \emph{Phys. Rev. E} \textbf{107}, 054101 (2023) 
	
	\item  Stability of branched tubular membrane structures\\
	M. Jung, \textbf{G. Jung}, F. Schmid, \emph{Phys. Rev. Lett.} \textbf{130}, 148401 (2023)
	
	\item  Passive probe particle in an active bath: can we tell it is out of equilibrium?\\
	J. Shea, \textbf{G. Jung}, F. Schmid, \emph{Soft Matter} \textbf{18}, 6965 (2022)
	
	\item  Structural properties of liquids in extreme confinement\\
	\textbf{G. Jung}, T. Franosch, \emph{Phys. Rev. E} \textbf{106}, 014614 (2022) 
	
	\item  Layering and Packing in Confined Colloidal Suspensions (Open Access)\\
	A. Villada-Balbuena, \textbf{G. Jung}, A. B. Zuccolotto-Bernez, T. Franosch, S. Egelhaaf, \emph{Soft Matter} \textbf{18}, 4699 (2022)
	
	\item  Non-Markovian systems out of equilibrium: Exact results for two routes of coarse graining (Invited Special Issue: \emph{Emerging Leaders 2021})\\
	\textbf{G. Jung}, \emph{J. Phys.: Condens. Matter} \textbf{34}, 204004 (2022)
	
					\item  Fluctuation-dissipation relations far from equilibrium: A case study (Open Access)\\
	\textbf{G. Jung}, F. Schmid, Soft Matter \textbf{17}, 6413 (2021)
				\item  Introducing memory in coarse-grained molecular simulations (Review Article,Open Access)\\
	V. Klippenstein, M. Tripathy, \textbf{G. Jung}, F. Schmid, N. van der Vegt, JCPB \textbf{125}, 4931 (2021)
			\item  Tagged-particle motion in quasi-confined colloidal hard-sphere liquids\\
	L. Schrack, C. F. Petersen, \textbf{G. Jung}, M. Caraglio, T. Franosch, J. Stat. Mech \textbf{043301} (2021)
			\item  Model reduction techniques for the computation of extended Markov parameterizations for generalized Langevin equations (Open Access)\\
	 N. Bockius, J. Shea, \textbf{G. Jung}, F. Schmid, M. Hanke, JCMP \textbf{33}, 214003 (2021) 
		\item Wall slip and bulk yielding in soft particle suspensions\\
	\textbf{G. Jung}, S. Fielding, Journal of Rheology \textbf{65}, 199 (2021)
		\item An improved integration scheme for mode-coupling-theory equations\\
	M. Caraglio, L. Schrack, \textbf{G. Jung}, T. Franosch, \emph{Comm. Comp. Phys.} \textbf{29}, 628 (2021)
		\item Tagged-particle dynamics in confined colloidal liquids\\
	\textbf{G. Jung}, L. Schrack, T. Franosch, \emph{Phys. Rev. E} \textbf{102}, 032611 (2020)
	\item Confinement-induced demixing and crystallization\\
	\textbf{G. Jung}, C. F. Petersen, \emph{Phys. Rev. Res.} \textbf{2}, 033207 (2020)
		\item Dynamic properties of quasi-confined colloidal hard-sphere liquids near the glass transition\\
	L. Schrack, C. F. Petersen, \textbf{G. Jung}, M. Caraglio, T. Franosch, \emph{J. Stat. Mech.} 093301 (2020) 
	\item Dynamical properties of densely packed confined hard-sphere fluids\\
	\textbf{G. Jung}, M. Caraglio, L. Schrack, T. Franosch, \emph{Phys. Rev. E} \textbf{102}, 012612 (2020)
	\item Scaling equations for mode-coupling theories with multiple decay channels\\
	\textbf{G. Jung}, T. Voigtmann, T. Franosch, \emph{J. Stat. Mech.} \textbf{7}, 073301 (2020)
	\item Frequency-dependent dielectric polarizability of flexible polyelectrolytes in electrolyte solution: A Dissipative Particle Dynamics simulation \\
	\textbf{G. Jung}, S. Kasper, F. Schmid, \emph{J. of the Electrochemical Soc.} \textbf{166}, B3194 (2019)
	\item Generalized Langevin dynamics: Construction and numerical integration of non-Markovian particle-based models\\
\textbf{	G. Jung}, M. Hanke, F. Schmid, \emph{Soft Matter} \textbf{14}, 9368 (2018).
	\item Frequency-dependent hydrodynamic interactions between two solid spheres\\
	\textbf{G. Jung}, F. Schmid, \emph{Phys. of Fluids} \textbf{29}, 126101 (2017)
	\item Iterative reconstruction of memory kernels  \\
	\textbf{G. Jung}, M. Hanke, F. Schmid, \emph{J. Chem. Theory and Comp.} \textbf{13}, 2481 (2017).
	\item Computing bulk and shear viscosities from simulations of fluids with dissipative and stochastic interactions\\
\textbf{	G. Jung}, F. Schmid, \emph{J. Chem. Phys.} \textbf{144}, 204104 (2016)
\end{enumerate}



\subsubsection*{Preprints}

\begin{enumerate}
	\item Roadmap on machine learning glassy liquids\\
\textbf{G. Jung} \emph{et al.},  preprint arXiv:2311.14752 

\item How boundary interactions dominate emergent driving of passive probes in active matter\\
J. Shea, \textbf{G. Jung}, F Schmid, preprint arXiv:2401.09227
\end{enumerate}

\subsubsection*{Review activities}
 Reviewer for international journals: Physical Review Letters, Communications Physics, Journal of Chemical Physics, Europhysics Letters, Physical Review E, Journal of Statistical Physics,  Frontiers in Physics, Molecular Simulation, Macromolecular Theory and Simulations


